Stable individual differences in strategies within, but not between, visual search tasks

### 2019-10-24 Manuscript/manuscript.tex
nearly finished revisions.

There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise, but the test-retest correlations and within-task correlations on each of the individual visual search task metrics rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation for the lack of correlation. One might have expected reaction time to be at least modestly correlated from one search task to the next, as a general factor like an individual's speed-accuracy trade-off, or motivation might lead to better or worse overall performance, but there was no relationship. Although the tasks in this experiment all have visual search in common, they also have unique aspects that appear to have resonated with particular individuals' strengths, and not others. Our definition of a successful strategy in the SHLS task was fixating the locations that provide new information. In the ACVS task, a successful strategy meant appropriately altering search goals to match changes in the environment. In the MCFT task, success involved minimizing cognitive load by minimizing target switching. Each of these tasks taps into unique aspects of visual search strategies, and performance on one has little bearing on the others.

Individual differences pose a challenge for efforts to devise a comprehensive model of visual search. Our understanding of the mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure effects on averaged performance. This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.  \cite{treisman1980}; how attentional control settings filter distractors \cite(e.g.){folk1992,yantis1999}; and biases in attention, such as a bias towards unexplored locations \cite(e.g.){klein2000}. For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance. In the original SHLS study, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \cite{najemnik-geisler2008}, versus a stochastic  \cite{clarke2016}, model. Considering only the average performance, the stochastic model was a good explanation. Underlying that average performance, however, was a spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither. The original question needed to be refined: for whom is search optimal and for whom is it stochastic? Our approach in this experiment puts into practice several of the recommendations of Clarke et al. \citeyear{clarke2019}, who suggest that a focus on accounting for variance, in addition to interpreting average patterns, will lead to important new insights. Another recommendation from that paper is to examine the generalizability of conclusions across paradigms, which we have also done here. Taking this further, it would be interesting to examine the extent to which the results of each of these search paradigms would scale to similar, but more familiar and realistic, contexts. The current findings add even further challenges for researchers, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.

>>>>

There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise, but the test-retest correlations and within-task correlations on each of the individual visual search task metrics rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation for the lack of correlation. One might have expected reaction time to be at least modestly correlated from one search task to the next, as a general factor like an individual's speed-accuracy trade-off, or motivation might lead to better or worse overall performance, but there was no relationship. Although the tasks in this experiment all have visual search in common, they also have unique aspects that appear to have resonated with particular individuals' strengths, and not others. Our definition of a successful strategy in the SHLS task was fixating the locations that provide new information. In the ACVS task, a successful strategy meant appropriately altering search goals to match changes in the environment. In the MCFT task, success involved minimizing cognitive load by minimizing target switching. Each of these tasks taps into unique aspects of visual search strategies, and performance on one has little bearing on the others. \textcolor{blue}{For example, recent work on the ACVS task suggests that that enumerating the color subsets plays an important role in achieving the optimal strategy \cite{hansen2019taking}. Clearly this step isn't required in the SHLS search, as the stimulus consists of grey lines. Instead, participants have to judge the variability in orientation across the scene. }

Individual differences pose a challenge for efforts to devise a comprehensive model of visual search. Our understanding of the mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure effects on averaged performance. This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.  \cite{treisman1980}; how attentional control settings filter distractors \cite(e.g.){folk1992,yantis1999}; and biases in attention, such as a bias towards unexplored locations \cite(e.g.){klein2000}. For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance. In the original SHLS study, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal \cite{najemnik-geisler2008}, versus a stochastic \cite{clarke2016}, model. Considering only the average performance, the stochastic model was a good explanation. Underlying that average performance, however, was a spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither. The original question needed to be refined: for whom is search optimal and for whom is it stochastic? \textcolor{blue}{Our approach in this experiment puts into practice several of the recommendations of Clarke et al. \citeyear{clarke2019}, who suggest that a focus on accounting for variance, in addition to interpreting average patterns, will lead to important new insights. Another recommendation from that paper is to examine the generalizability of conclusions across paradigms, which we have also done here. Taking this further, it would be interesting to examine the extent to which the results of each of these search paradigms would scale to similar, but more familiar and realistic, contexts. Leber \& Irons \citeyear{leber-irons2019} have summarised a range of methods and measures that can be used to study attention strategy, (e.g. saccadic choice, speed-accuracy tradeoff, meta-cognitive report, etc).} The current findings add even further challenges for researchers, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.
